---
title: "False belief understanding across children and adults during exposure to mean versus nice behaviors"
author: "Lily Tsoi, email: ltsoi@princeton.edu"
date: '`r format(Sys.time(), "%B %d, %Y")`'
output:
  html_notebook: 
    code_folding: show
    theme: flatly
    highlight: tango
    toc: yes
    toc_depth: 6
    toc_float: no
---

## Install packages

```{r, message=FALSE, results="hide", warning=FALSE}
packages <- c("tidyverse", "Rmisc", "optimx", "emmeans", "sjPlot", "knitr", "TOSTER", "ordinal", "lme4", "simr")
packages_new <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(packages_new)) install.packages(packages_new)
lapply(packages,library,character.only=T)

# set palette color for figures
palette(c("#f6bd60", "#f5cac3", "#84a59d"))

```

## Import and organize data

### Study 1

```{r}

file <- "Data_children.csv"

# read file
df_child_orig <- read.csv(file, na.strings=c("","NA","No answer"))

# make sure variables are read properly (numeric as numeric, factor as factor). use str(df_child) to examine variables
df_child <- df_child_orig
df_child$Age <- as.numeric(as.character(df_child$Age))
df_child$Subject.Number <- as.factor(as.character(df_child$Subject.Number))

# scale Age
df_child$Age_scaled <- scale(df_child$Age)

# only limit the data to children ages 3, 4, and 5
df_child <- subset(df_child, Age >= 3 & Age < 6)
df_child <- droplevels(df_child)

# turn categorical age to ordered variable
df_child$Age.Category <- ordered(factor(df_child$Age.Category, levels=c("three","four","five"))) # specify order of levels

# convert nonsense response to NA
df_child$Is.Sally.a.nice.girl.or.not.a.nice.girl.[df_child$Is.Sally.a.nice.girl.or.not.a.nice.girl. == "No"] <- NA

# create new variables

# variables related to accuracy
df_child$Think[df_child$Where.does.Sally.think.her.ball.is. == 'Basket'] <- 1
df_child$Think[df_child$Where.does.Sally.think.her.ball.is. == 'Closet'] <- 0
df_child$Look[df_child$Where.will.Sally.look. == 'Basket'] <- 1
df_child$Look[df_child$Where.will.Sally.look. == 'Closet'] <- 0

# variables related to congruence
df_child$Should.Anne.and.Sally.be.friends.congruent[df_child$Should.Anne.and.Sally.be.friends. == 'Yes' & df_child$Nice_Mean == 'Nice'] <- 1
df_child$Should.Anne.and.Sally.be.friends.congruent[df_child$Should.Anne.and.Sally.be.friends. == 'No' & df_child$Nice_Mean == 'Mean'] <- 1
df_child$Should.Anne.and.Sally.be.friends.congruent[df_child$Should.Anne.and.Sally.be.friends. == 'Yes' & df_child$Nice_Mean == 'Mean'] <- 0
df_child$Should.Anne.and.Sally.be.friends.congruent[df_child$Should.Anne.and.Sally.be.friends. == 'No' & df_child$Nice_Mean == 'Nice'] <- 0
df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl.congruent[df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl == 'Nice' & df_child$Nice_Mean == 'Nice'] <- 1
df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl.congruent[df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl == 'Mean' & df_child$Nice_Mean == 'Mean'] <- 1
df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl.congruent[df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl == 'Nice' & df_child$Nice_Mean == 'Mean'] <- 0
df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl.congruent[df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl == 'Mean' & df_child$Nice_Mean == 'Nice'] <- 0
df_child$Should.Anne.and.Sally.be.friends.congruent <- as.factor(df_child$Should.Anne.and.Sally.be.friends.congruent)
df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl.congruent <- as.factor(df_child$Is.Anne.a.nice.girl.or.not.a.nice.girl.congruent)

# drop unused levels from factors
df_child <- droplevels(df_child)
df_child <- mutate(df_child, Prop_correct = (Think + Look)/2)

# turn question type into a factor
df_child_quest <- df_child %>% gather(key = Question, value = Correct, Think, Look)
df_child_quest$Question <- as.factor(df_child_quest$Question)

# create variable for counterbalancing order
df_child_quest$Counterbalancing_order[df_child_quest$Question == "Look" & df_child_quest$Order.of.think.and.look.asked == "Look 1st asked"] <- "first"
df_child_quest$Counterbalancing_order[df_child_quest$Question == "Think" & df_child_quest$Order.of.think.and.look.asked == "Think 1st asked"] <- "first"
df_child_quest$Counterbalancing_order[df_child_quest$Question == "Look" & df_child_quest$Order.of.think.and.look.asked == "Think 1st asked"] <- "second"
df_child_quest$Counterbalancing_order[df_child_quest$Question == "Think" & df_child_quest$Order.of.think.and.look.asked == "Look 1st asked"] <- "second"
df_child_quest$Counterbalancing_order <- as.factor(df_child_quest$Counterbalancing_order)

# subset by usable data
df_child_Sally <- subset(df_child, Usable_Final_Sally == 1)
df_child_quest_Sally <- subset(df_child_quest, Usable_Final_Sally == 1)

# subset data by comp check
df_child_congruent <- subset(df_child_Sally, Is.Anne.a.nice.girl.or.not.a.nice.girl.congruent == 1)
df_child_quest_congruent <- subset(df_child_quest_Sally, Is.Anne.a.nice.girl.or.not.a.nice.girl.congruent == 1)

```

### Study 2

```{r}

# read hdr
file_qualtrics_pre <- list.files(getwd(), pattern="pre.csv")
df_adults_long <- read.csv(file_qualtrics_pre, header=TRUE, nrows=1, as.is = TRUE, na.strings = c("-99","", "NA"))
df_adults_long <- df_adults_long[FALSE,]

# bind all three versions
for (f in c("2pre", "2a", "2b")) {
  file_qualtrics_v <- list.files(getwd(), pattern=paste0("Data_adults_Study", f, '.csv'))
  df_tmp <- read.csv(file_qualtrics_v, header=TRUE, as.is = TRUE, na.strings = c("-99","","NA"))
  df_tmp$version <- f
  df_adults_long <- bind_rows(df_adults_long, df_tmp)
}

turn_to_factor <- c("RecordedDate", "ResponseId", "Gender", "condition", "Question", "version")
df_adults_long <- df_adults_long %>% mutate_at(turn_to_factor, factor)
df_adults_long$trial <- factor(df_adults_long$trial, ordered = TRUE, levels = as.character(1:max(unique(df_adults_long$trial))))
df_adults_long$Nice <- factor(df_adults_long$Nice, ordered = TRUE, levels = c("not at all\n1", "2", "3", "4", "5", "6", "very\n7"))
levels(df_adults_long$Nice) <- list("1"="not at all\n1", "2"="2", "3"="3", "4"="4", "5"="5", "6"="6", "7"="very\n7")
df_adults_long$item <- factor(df_adults_long$item, levels = as.character(1:max(unique(df_adults_long$item))))

# re-code condition
df_adults_long$condition <- recode(df_adults_long$condition, cooperation = "nice", competition = "mean")

# scale age
df_adults_long$Age_scaled <- scale(df_adults_long$Age, center = TRUE, scale = TRUE)

# for descriptive stats on demographics
df_adults_dem <- df_adults_long

# remove attention check as item
df_adults_long <- df_adults_long %>% filter(!condition == "attention")
df_adults_long <- droplevels(df_adults_long)
df_adults_2pre <- subset(df_adults_long, version == "2pre")
df_adults_2a <- subset(df_adults_long, version == "2a")
df_adults_2b <- subset(df_adults_long, version == "2b")

```

## Study 1

### Descriptive statistics

#### Sample demographics

##### Overall

```{r}

by(df_child_Sally[,c("Age.Category", "Gender")], df_child_Sally[,c("Age.Category")], summary)

```

##### By condition

```{r}

by(df_child_Sally[,c("Age.Category", "Gender", "Nice_Mean", "Age")], df_child_Sally[,c("Nice_Mean")], summary)

```

##### By question order

The order in which the two main questions ("Where will Sally look?" and "Where does Sally think her ball is?") were presented was counterbalanced across participants. However, there are concerns that because of high exclusion rates, the final count for one order could be higher than the other. We examine that here.

```{r}

by(df_child_Sally[,c("Age.Category", "Gender", "Nice_Mean", "Order.of.think.and.look.asked")], df_child_Sally[,c("Order.of.think.and.look.asked")], summary)

```

##### By comprehension question (congruent with condition or not)

```{r}

by(df_child_Sally[,c("Age.Category", "Gender", "Nice_Mean", "Is.Anne.a.nice.girl.or.not.a.nice.girl.congruent")], df_child_Sally[,c("Nice_Mean")], summary)

```

##### By age category

```{r}

df_age <- summarySE(df_child_Sally, measurevar = "Age", groupvars = c("Age.Category", "Nice_Mean"))

age_1 <- subset(df_child_Sally, Nice_Mean == 'Nice')
age_2 <- subset(df_child_Sally, Nice_Mean == 'Mean')


for (age_cat in c("three", "four", "five")) {
  print(age_cat)
  
  # perform t-test for each age category
  print(t.test(age_1$Age[which(age_1$Age.Category == age_cat)], age_2$Age[which(age_2$Age.Category == age_cat)], alternative="two.sided"))
  
  
  # calculate cohen's d
  g1_m <- df_age$Age[which(df_age$Nice_Mean == "Nice" & df_age$Age.Category == age_cat)]
  g1_sd <- df_age$sd[which(df_age$Nice_Mean == "Nice" & df_age$Age.Category == age_cat)]
  g2_m <- df_age$Age[which(df_age$Nice_Mean == "Mean" & df_age$Age.Category == age_cat)]
  g2_sd <- df_age$sd[which(df_age$Nice_Mean == "Mean" & df_age$Age.Category == age_cat)]
  
  d <- (g2_m - g1_m) / sqrt((g1_sd^2 + g2_sd^2)/2)
  print(sprintf("Cohen's d for Age Category %s: %0.3f", age_cat, d))
  }



```


### Figures

#### Figure 1. Condition differences

##### (A) By condition

```{r}

ggplot(df_child_Sally, aes(y = Prop_correct, x = Nice_Mean)) +
  stat_summary(fun.data="mean_cl_boot", fun.args=list(B = 10000), na.rm=TRUE, position=position_dodge(width=0.3), size=1) +
  ylim (0,1) +
  ylab ("% of children answering correctly") +
  xlab ("Condition") +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"),
        axis.title.y=element_text(margin=margin(r=20)),
        axis.title.x=element_text(margin=margin(t=20)),
        legend.text=element_text(size=12),
        legend.title=element_text(size=12,face="bold"),
        legend.key.size=unit(3, "lines"),
        strip.text=element_text(size=14, face="bold"),
        panel.grid.major.x=element_blank(),
        panel.grid.major.y=element_blank(),
        plot.title = element_text(hjust = 0.5))

```

##### (B) By condition and age

```{r}

ggplot(df_child_Sally, aes(y = Prop_correct, x = Nice_Mean, color= Age.Category)) +
  stat_summary(fun.data="mean_cl_boot", fun.args=list(B = 10000), na.rm=TRUE, position=position_dodge(width=0.3), size=1) +
  ylim (0,1) +
  ylab ("% of children answering correctly") +
  xlab ("Condition") +
  scale_color_manual(values = palette(), name="Age Category") +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"),
        axis.title.y=element_text(margin=margin(r=20)),
        axis.title.x=element_text(margin=margin(t=20)),
        legend.text=element_text(size=12),
        legend.title=element_text(size=12,face="bold"),
        legend.key.size=unit(3, "lines"),
        strip.text=element_text(size=14, face="bold"),
        panel.grid.major.x=element_blank(),
        panel.grid.major.y=element_blank(),
        plot.title = element_text(hjust = 0.5))

```

#### Responses to Questions 3-5

##### (A) Should Anne and Sally be friends?

```{r, warning=FALSE}
t_friends <- df_child_Sally %>%
  group_by(Age.Category, Nice_Mean, Should.Anne.and.Sally.be.friends.) %>%
  dplyr::summarise(n = n())
t_friends <- left_join(t_friends, summarise_at(t_friends, vars(n), sum), by=c("Age.Category", "Nice_Mean")) %>%
  mutate(prop = n.x / n.y)
  
t_friends$Should.Anne.and.Sally.be.friends. <- factor(t_friends$Should.Anne.and.Sally.be.friends., levels=c("No","Yes","Does not know", "NA")) # specify order of level

ggplot(t_friends, aes(y=prop, x=Nice_Mean, fill=Should.Anne.and.Sally.be.friends.)) +
  geom_bar(stat="identity", colour="black") +
  geom_text(aes(label = round(prop, digits=2)), position=position_stack(vjust=0.5)) +
  facet_wrap(~Age.Category, ncol=3) +
  xlab("Condition - Mean or Nice Anne") +
  ylab("Proportion") +
  ggtitle("Should Anne and Sally be friends?") +
  scale_fill_manual(values = c("#5998c5","#b5d8cc", "#d5c6e0", "#ceeddb"), name="", labels=c("No", "Yes", "Does not know", "No response")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

##### (B) Is Anne a nice girl or not a nice girl?

```{r, warning=FALSE}

t_anne <- df_child_Sally %>%
  group_by(Age.Category, Nice_Mean, Is.Anne.a.nice.girl.or.not.a.nice.girl) %>%
  dplyr::summarise(n = n())
t_anne <- left_join(t_anne, summarise_at(t_anne, vars(n), sum), by=c("Age.Category", "Nice_Mean")) %>%
  mutate(prop = n.x / n.y)

ggplot(t_anne, aes(y=prop, x=Nice_Mean, fill=Is.Anne.a.nice.girl.or.not.a.nice.girl)) +
  geom_bar(stat="identity", colour="black") +
  geom_text(aes(label = round(prop, digits=2)), position=position_stack(vjust=0.5)) +
  facet_wrap(~Age.Category, ncol=3) +
  xlab("Condition - Mean or Nice Anne") +
  ylab("Proportion") +
  ggtitle("Is Anne a nice girl or not a nice girl?") +
  scale_fill_manual(values = c("#bfbfbf", "#ffe5d9", "#4b5358"), name="", labels=c("Not Nice", "Nice", "No response")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

##### (C) Is Sally a nice girl or not a nice girl?

```{r, warning=FALSE}
t_sally <- df_child_Sally %>%
  group_by(Age.Category, Nice_Mean, Is.Sally.a.nice.girl.or.not.a.nice.girl.) %>%
  dplyr::summarise(n = n())
t_sally <- left_join(t_sally, summarise_at(t_sally, vars(n), sum), by=c("Age.Category", "Nice_Mean")) %>%
  mutate(prop = n.x / n.y)

ggplot(t_sally, aes(y=prop, x=Nice_Mean, fill=Is.Sally.a.nice.girl.or.not.a.nice.girl.)) +
  geom_bar(stat="identity", colour="black") +
  geom_text(aes(label = round(prop, digits=2)), position=position_stack(vjust=0.5)) +
  facet_wrap(~Age.Category, ncol=3) +
  xlab("Condition - Mean or Nice Anne") +
  ylab("Proportion") +
  ggtitle("Is Sally a nice girl or not a nice girl?") +
  scale_fill_manual(values = c("#bfbfbf", "#ffe5d9", "#85baa1", "#4b5358"), name="", labels=c("Not Nice", "Nice", "Other", "No response")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

#### Figure S2. Performance by Question Type

```{r, fig.height = 3}

ggplot(df_child_quest_Sally, aes(y = Correct, x = Age.Category, color= Question)) +
  stat_summary(fun.data="mean_cl_boot", position=position_dodge(0.3)) + 
    ylim (0,1) +
    ylab ("Proportion of children answering correctly") +
    xlab ("Age Category") +
    scale_color_manual(values = c("#AFC0E8","#1F49AB"), labels = c("Where will Sally look?", "Where does Sally think her ball is?")) +
    theme_bw() +
    theme(axis.text=element_text(size=12),
          axis.title=element_text(size=14,face="bold"),
          axis.title.y=element_text(margin=margin(r=20)),
          axis.title.x=element_text(margin=margin(t=20)),
          legend.text=element_text(size=12),
          legend.title=element_text(size=12,face="bold"),
          legend.key.size=unit(3, "lines"),
          strip.text=element_text(size=14, face="bold"),
          panel.grid.major.x=element_blank(),
          panel.grid.major.y=element_blank(),
          plot.title = element_text(hjust = 0.5))
```

### Analyses

Variables we care about:

- Correct (Incorrect=0, Correct=1)
- Condition (Mean, Nice)
- Age Category (3s, 4s, 5s)
- Question Type ("Where will Sally look?", "Where does Sally think her ball is?")
- Is-Anne-Nice? (Mean, Nice)
- Counterbalancing Order ("Look" first, "Think" first)
- Gender (F,M)

The same analyses were performed for:
- all usable data ("all")
- data from people responding to the question "Is Anne a nice girl or not a nice girl?" in a manner congruent with the condition to which they were assigned ("congruent")

For both sets of data, we performed the same analyses using age as a categorical variable (Age Category) and age as a continuous variable (Age).

```{r}

var_dat <- c("all", "congruent")
var_age <- c("Age.Category", "Age_scaled")

for (d in var_dat) {
  if (exists("dat_model")) {rm(dat_model)}
  if (d == "all") {
    cat('\n\n*** All usable data ***\n\n')
    dat_model <- df_child_quest_Sally
  } else if (d == "congruent") {
    cat('\n\n*** Congruent data only ***\n\n')
    dat_model <- df_child_quest_congruent
  }
  for (a in var_age) {
    cat(paste0('\n\n--- Using the following age variable: ', a, ' ---\n\n'))
    dat_model$Age_model <- dat_model[,a]
    
    model <- glmer(Correct ~ Nice_Mean + Question + Age_model + Counterbalancing_order + Gender +
                    Nice_Mean:Question +
                    Nice_Mean:Age_model +
                    Nice_Mean:Counterbalancing_order +
                    Question:Age_model +
                    Nice_Mean:Question:Age_model +
                    (1 | Subject.Number),
                  data = dat_model,
                  family = binomial,
                  control = glmerControl(optimizer = 'optimx', optCtrl = list(method = 'bobyqa'))) # methods: nlminb, bobyqa
    
    # remove 3-way interaction
    model.1 <- update(model, . ~ . -Nice_Mean:Question:Age_model)
    print(drop1(model.1, test="Chisq"))
    # remove 2-way interactions with Condition
    model.2 <- update(model.1, . ~ . -Nice_Mean:Question -Nice_Mean:Age_model -Nice_Mean:Order.of.think.and.look.asked -Nice_Mean:Gender -Nice_Mean:Counterbalancing_order -Question:Counterbalancing_order)
    print(drop1(model.2, test="Chisq"))
    
    print(summary(model))
    print(tab_model(model, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_1_', d, '_', a, '_fb.html')))

    if (a == "Age.Category") {
      cat("\n\nCondition by Age Category\n\n")
      print(emmeans(model, pairwise ~ Nice_Mean | Age_model, type="response")$contrast)
      cat("\nQuestion by Age Category\n\n")
      print(emmeans(model, pairwise ~ Question | Age_model, type="response")$contrast)
    }
    cat("\n\nCondition by Question Type\n\n")
    print(emmeans(model, pairwise ~ Nice_Mean | Question, type="response")$contrast)
    cat("\n\nCondition by Counterbalancing Order\n\n")
    print(emmeans(model, pairwise ~ Nice_Mean | Counterbalancing_order, type="response")$contrast)
    
  }
}

```

## Study 2


### Study 2 combining Study 2a and 2b

#### Descriptives

##### Sample demographics

```{r}

print("With no exclusions")

dem_noexcl <- subset(df_adults_dem, condition == "attention") %>% distinct_at(c("ResponseId", "Age", "Gender"))

summary(dem_noexcl[c("Age", "Gender")])

print("With exclusions")

dem <- subset(df_adults_dem, condition == "attention" & correct == TRUE) %>% distinct_at(c("ResponseId", "Age", "Gender"))

summary(dem[c("Age", "Gender")])

```
##### By condition

```{r}

dem_by_subj <- summarySE(subset(df_adults_long, version == "2a" | version == "2b"), measurevar = "correct", groupvars = c("ResponseId", "condition"))
with(dem_by_subj, table(condition))

dem_count <- count(dem_by_subj, vars = c("correct", "condition"))
dem_count
sum(dem_count$freq)

```

##### Figure 2. Condition differences

```{r, fig.width = 5}

df_adults_plot <- summarySE(subset(df_adults_long, version == "2a" | version == "2b"), measurevar = "correct", groupvars = c("ResponseId", "condition"))

ggplot(df_adults_plot, aes(y = correct, x = condition)) +
  geom_violin() +
  stat_summary(fun.data="mean_cl_boot", fun.args=list(B = 10000), na.rm=TRUE, position=position_dodge(width=0.3), size=0.5) +
  ylim (0,1) +
  ylab ("Proportion of questions answered correctly") +
  xlab ("Condition") +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"),
        axis.title.y=element_text(margin=margin(r=20)),
        axis.title.x=element_text(margin=margin(t=20)),
        legend.text=element_text(size=12),
        legend.title=element_text(size=12,face="bold"),
        legend.key.size=unit(3, "lines"),
        plot.title = element_text(hjust = 0.5))
```

#### Analyses

##### With the two full versions

###### Response on the false belief question

```{r}

m2_full <- glmer(correct ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=subset(df_adults_long, version == "2a" | version == "2b"),
                  family=binomial, 
                  control = glmerControl(optimizer = 'optimx', optCtrl = list(method = 'bobyqa'))) # methods: nlminb, bobyqa

m3_full <- update(m2_full, . ~ . -condition)

anova(m2_full, m3_full, test="Chisq")

print(summary(m2_full))

print(tab_model(m2_full, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_2ab_fb.html')))

print(emmeans(m2_full, pairwise ~ condition, type="response")$contrast)
```

###### Sensitivity analysis

```{r}

# Sensitivity power analysis for the fixed N.
# Estimating the power to detect ES from .4 to .48 for the effect of condition
N <- 279 

es.vect <- c(.28, .29, .30)
pwr <- NA
m_sensitive1 <- m2_full
m_sensitive2 <- m3_full
for(i in 1:length(es.vect)){
  fixef(m_sensitive1)["conditionnice"] <- es.vect[i]
  pwr[i] <- round(as.numeric(summary(powerSim(m_sensitive1, test = compare(m_sensitive2, method = "lr"), nsim = 1000)))[3],3)
  print(pwr[i])
}


```

###### RT for false belief question

```{r}

m2_full_RT <- lmer(TF_RT ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=subset(df_adults_long, version == "2a" | version == "2b"))

print(summary(m2_full_RT))

print(tab_model(m2_full_RT, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_2ab_fb_RT.html')))

drop1(m2_full_RT, test="Chisq")

```

###### Removing ceiling performance

Response on the false belief question

```{r}

df_adults_noceil <- df_adults_long %>% filter(version == "2a" | version == "2b") %>% group_by(ResponseId, condition) %>% dplyr::mutate(correct_prop = mean(correct)) %>% ungroup() %>% filter(correct_prop != 1)

m2_full_noceil <- glmer(correct ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_noceil,
                  family=binomial, 
                  control = glmerControl(optimizer = 'optimx', optCtrl = list(method = 'bobyqa'))) # methods: nlminb, bobyqa

anova(m2_full_noceil, update(m2_full_noceil, . ~ . -condition), test="Chisq")

print(summary(m2_full_noceil))

print(tab_model(m2_full_noceil, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_2ab_fb_noceil.html')))

print(emmeans(m2_full_noceil, pairwise ~ condition, type="response")$contrast)
```

## Study 2-pre (Supp Mat)

### Descriptives

#### Sample demographics

```{r}

print("With no exclusions")

dem_2pre_noexcl <- subset(df_adults_dem, version == "pre" & condition == "nice") %>% distinct_at(c("ResponseId", "Age", "Gender"))

summary(dem_2pre_noexcl[c("Age", "Gender")])

```

### Analyses

#### Manipulation check

```{r}

df_adults_2pre_m <- subset(df_adults_2pre, !is.na(condition) & !is.na(Gender) & !is.na(Age) & !is.na(ResponseId) & !is.na(item) & !is.na(Nice))

m2pre_full_check <- clmm(Nice ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_2pre_m)

drop1(m2pre_full_check, test="Chisq")

print(emmeans(m2pre_full_check, pairwise ~ condition, type="response")$contrast, mode="mean.class")

```

#### Response on false belief question

```{r}

df_adults_2pre_m <- subset(df_adults_2pre, !is.na(condition) & !is.na(Gender) & !is.na(Age) & !is.na(ResponseId) & !is.na(item) & !is.na(correct))

m2pre_full <- glmer(correct ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_2pre_m,
                  family=binomial, 
                  control = glmerControl(optimizer = 'optimx', optCtrl = list(method = 'bobyqa'))) # methods: nlminb, bobyqa

drop1(m2pre_full, test="Chisq")

print(summary(m2pre_full))

print(tab_model(m2pre_full, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_2pre_fb.html')))

print(emmeans(m2pre_full, pairwise ~ condition, type="response")$contrast)

```

#### RT for false belief question

```{r}

df_adults_2pre_m <- subset(df_adults_2pre, !is.na(condition) & !is.na(Gender) & !is.na(Age) & !is.na(ResponseId) & !is.na(item) & !is.na(TF_RT))

m2pre_full_RT <- lmer(TF_RT ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_2pre_m)

print(summary(m2pre_full_RT))

print(tab_model(m2pre_full_RT, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_2pre_fb_RT.html')))

drop1(m2pre_full_RT, test="Chisq")

print(emmeans(m2pre_full_RT, pairwise ~ condition, type="response")$contrast)

```

## Study 2a

### Descriptives

#### Sample demographics

```{r}

print("With no exclusions")

dem_2a_noexcl <- subset(df_adults_dem, version == "2a" & condition == "attention") %>% distinct_at(c("ResponseId", "Age", "Gender"))

summary(dem_2a_noexcl[c("Age", "Gender")])

print("With exclusions")

dem_2a <- subset(df_adults_dem, version == "2b" & condition == "attention" & correct == TRUE) %>% distinct_at(c("ResponseId", "Age", "Gender"))

summary(dem_2a[c("Age", "Gender")])

```

### Analyses

#### Manipulation check

```{r}

m2a_full_check <- clmm(Nice ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_2a)

drop1(m2a_full_check, test="Chisq")

print(emmeans(m2a_full_check, pairwise ~ condition, type="response")$contrast, mode="mean.class")

```

#### Response on false belief question

```{r}

m2a_full <- glmer(correct ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_2a,
                  family=binomial, 
                  control = glmerControl(optimizer = 'optimx', optCtrl = list(method = 'bobyqa'))) # methods: nlminb, bobyqa

drop1(m2a_full, test="Chisq")

print(summary(m2a_full))

print(tab_model(m2a_full, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_2a_fb.html')))

print(emmeans(m2a_full, pairwise ~ condition, type="response")$contrast)

```

#### RT for false belief question

```{r}

m2a_full_RT <- lmer(TF_RT ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_2a)

print(summary(m2a_full_RT))
print(tab_model(m2a_full_RT, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_2a_fb_RT.html')))

drop1(m2a_full_RT, test="Chisq")

print(emmeans(m2a_full_RT, pairwise ~ condition, type="response")$contrast)

```

## Study 2b

### Descriptives

#### Sample demographics

```{r}

print("With no exclusions")

dem_2b_noexcl <- subset(df_adults_dem, version == "2b" & condition == "attention") %>% distinct_at(c("ResponseId", "Age", "Gender"))

summary(dem_2b_noexcl[c("Age", "Gender")])

print("With exclusions")

dem_2b <- subset(df_adults_dem, version == "2b" & condition == "attention" & correct == TRUE) %>% distinct_at(c("ResponseId", "Age", "Gender"))

summary(dem_2b[c("Age", "Gender")])

```

### Analyses

#### Manipulation check

```{r}

m2b_full_check <- clmm(Nice ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_2b)

drop1(m2b_full_check, test="Chisq")

print(emmeans(m2b_full_check, pairwise ~ condition, type="response")$contrast, mode="mean.class")

```

#### Response on false belief question

```{r}

m2b_full <- glmer(correct ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_2b,
                  family=binomial, 
                  control = glmerControl(optimizer = 'optimx', optCtrl = list(method = 'bobyqa'))) # methods: nlminb, bobyqa

print(summary(m2b_full))
print(tab_model(m2b_full, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_2b_fb.html')))

drop1(m2b_full, test="Chisq")

print(emmeans(m2b_full, pairwise ~ condition, type="response")$contrast)

```

#### RT for false belief question

```{r}

m2b_full_RT <- lmer(TF_RT ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_2b)

print(summary(m2b_full_RT))
print(tab_model(m2b_full_RT, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_2b_fb_RT.html')))

drop1(m2b_full_RT, test="Chisq")

print(emmeans(m2b_full_RT, pairwise ~ condition, type="response")$contrast)

```

## With all three versions

##### Manipulation check

```{r}

df_adults_long_m <- subset(df_adults_long, !is.na(condition) & !is.na(Gender) & !is.na(Age) & !is.na(ResponseId) & !is.na(item) & !is.na(Nice))

m_all3_full_check <- clmm(Nice ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_long_m)

drop1(m_all3_full_check, test="Chisq")

print(emmeans(m_all3_full_check, pairwise ~ condition, type="response")$contrast, mode="mean.class")

```

##### Response on the false belief question

```{r}

m_all3_full <- glmer(correct ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_long,
                  family=binomial, 
                  control = glmerControl(optimizer = 'optimx', optCtrl = list(method = 'bobyqa'))) # methods: nlminb, bobyqa

anova(m_all3_full, update(m_all3_full, . ~ . -condition), test="Chisq")

print(summary(m_all3_full))
print(tab_model(m_all3_full, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_all3_fb.html')))

print(emmeans(m_all3_full, pairwise ~ condition, type="response")$contrast)
```

##### RT for false belief question

```{r}

df_adults_long_all <- subset(df_adults_long, !is.na(TF_RT) & !is.na(condition) & !is.na(Gender) & !is.na(Age))

m_all3_full_RT <- lmer(TF_RT ~ condition + Gender + Age +
                    (1|ResponseId) + (1|item),
                  data=df_adults_long_all)

print(summary(m_all3_full_RT))
print(tab_model(m_all3_full_RT, show.std = "std2", show.stat = TRUE, show.df = TRUE, file = paste0('model_all3_fb_RT.html')))

drop1(m_all3_full_RT, test="Chisq")

```
